---
title             : "Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions"
shorttitle        : "DOMAIN-SPECIFIC WORKING MEMORY AND SURPRISED EXPRESSIONS"

author: 
  - name          : "Nicholas R. Harp"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "nharp@huskers.unl.edu"
  - name          : "Maital Neta"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Nebraska-Lincoln"

authornote: |
  Nicholas R. Harp, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln
  Maital Neta, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln

abstract: |
  Individual differences in interpretations of emotional ambiguity are a useful tool for measuring affective biases. 
  
  While trait-like, these biases are also susceptible to experimental manipulations. In the present study, we capitalize on this malleability to expand on previous research suggesting that
  subjective interpretations are stable independently of cognitive load. 
  
  We tested the effects of working memory loads containing either neutral or emotional content on concurrent interpretations of surprised facial expressions.
  
  Here we show that interpretations of surprise are more negative during maintenance of working memory loads with emotional content compared to those with neutral content.
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "ambiguity, working memory, bias"
wordcount         : "X"

bibliography      : ["CANLab_UNL.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
### import z score updated function ###
source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/wilcox_test.R")
### code edits taken from : https://stats.stackexchange.com/questions/306841/z-score-on-wilcoxon-signed-ranks-test ###

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
## Facial expressions and individual differences
<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> Facial expressions are a mechanism for communicating emotion during social interactions. While the use of facial expressions as an information exchange may be universal [@izard_innate_1994], there are notable differences in interpretations of facial expressions [@green_factors_2018; @neta_corrugator_2009]. One such difference is in valence judgments of emotional facial expressions. The affective circumplex model posits that two independent neurophysiological systems give rise to emotional experience which are known as valence and arousal [@posner_circumplex_2005]. Valence is the inherent positive (i.e., pleasant) or negative (i.e., unpleasant) qualities of a stimulus, feeling, or state. Importantly, individuals differ in their tendency to interpret ambiguously valenced stimuli, such as a tempting food item or a surprised facial expression, as either positive or negative. <!-- Additionally, facial expressions can serve as ambiguously valenced stimuli. While most facial expressions send a clear social signal, this is not always the case. While a smile likely expresses a positive affective state, other cues are not so clear.--> This is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience. For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events. This affective bias is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to better understand this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013]. 

Previous work shows that valence bias is both a stable, trait-like measure [@neta_corrugator_2009], but also malleable due to its susceptibility to laboratory manipulations [@brown_cortisol_2017; @neta_through_2018; @neta_its_2018]. The trait-like nature of valence bias is useful for understanding chronic affective biases. Negativity biases, which may be adaptive in the short-term (e.g., heightened attention to negative stimuli in a potentially dangerous situation), can undermine healthy psychological functioning over time. For instance, negativity biases in memory and attention are related to an increased risk for psychopathology, such as depression and anxiety [@mathews_cognitive_2005]. <!-- suggesting the importance of understanding the factors that contribute to individuals' biases. --> Alternatively, the malleability of valence bias offers insight into mechanisms or interventions that may be capable of shifting bias. Several brief, laboratory interventions are known to shift bias. For example, instructing participants to slow responding will lead to more positive interpretations of ambiguity [@neta_dont_2016]. Alternatively, manipulating participant gaze to match that of extremely negative (or positive) individuals modulates individuals' bias [@neta_through_2018]. In short, valence bias offers insight into both state- and trait-like components of individuals behavior, but through what mechanisms might an individual arrive at either a positive or negative interpretation? 

## Initial negativity hypothesis
Myriad factors contribute to an individual's bias, but research suggests the initial interpretation is negative across people. Data supporting this initial negativity hypothesis come from many studies. As mentioned above, reaction times are faster for negative interpretations of ambiguous stimuli [@neta_dont_2016]. If negative interpretations occur faster than positive interpretations, then there may be an initial, automatic process resulting in the negativity. In turn, positive interpretations would require some override or regulation of this initial process. Supporting this idea, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, bias interpretations towards negativity [@neta_primacy_2010]. Again, this supports the automaticity of negative interpretations, and suggests that high spatial frequency components, which are processed later, may be helpful for overriding negativity. <!-- Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well. For example, shifting participants time perspectives shifts interpretations of ambiguous images as well [@neta_its_2018].--> Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation, when passively viewing surprised expressions, in brain regions recruited during emotion regulation of negative images [@petro_individual_2018]. Emotion regulation, and more specifically reappraisal, may be an underlying mechanism of a more positive valence bias. 

<!-- Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces.  In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases. -->
<!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser. When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep). This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias. -->
<!-- Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes. For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016]. Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010]. Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018]. <!-- Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. THIS NEEDS TO BE REWORKED In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.  -->

## Cognitive loads and task interference
Executive functions, including working memory, are related to successful self-regulation, and in turn emotion regulation [@hofmann_executive_2012]. Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues [-@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli. This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility. Other work has focused on the effects of moods or affective states on working memory performance. For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2013]. Similarly, active working memory processes may alter concurrent affective processes. For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli [@macnamara_working_2011]. Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@van_dillen_tuning_2009]. Additionally, following an anger induction, those with low trait rumination show faster blood pressure recovery when provided with a distractor task [@gerin_role_2006]. Together, these studies suggest a resource competition between cognitive and emotional processes; in other words, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes. 

While previous work suggests an inhibitory effect on some emotional responses during periods with high cognitive demands, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli. For instance, Schmeichel and colleagues [-@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli [@van_dillen_tuning_2009].<!--  Others have even measured symptoms during working memory maintenance of affective symptoms (i.e., typically increased negative affect), such as anxiety [@spangler_little_2017].--> However, many emotional appraisals, such as interpreting the valence of emotionally ambiguous stimuli, are more nuanced. <!-- For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals. This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.--> Maintenance of goal states can reduce performance on some components of executive functioning tasks [@shaw_dieting_2004], which is in line with Lavie and colleague's [-@lavie_load_2004] load theory. Cognitive load theory posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information. In turn, this means that more bottom-up, automatic processes (e.g., more readily processed perceptual input such as low spatial frequency information) might drive decisions under working memory loads.

## Domain-specific interference
Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of cognitive load and distractor interference effects in visual, spatial, and phonological domains [@burnham_components_2014]. Load interference effects may also transverse other domain components, such as maintaining emotional compared to neutral memory content. Emotional stimuli readily capture attention compared to neutral stimuli, and this is true even in participants with amygdala damage [@hodsoll_attentional_2011; @piech_attentional_2011]. Given the preference for emotional stimuli in the brain's information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals. Indeed, Kensigner and colleagues [-@kensinger_effect_2003] showed that negative emotional content slows performance on the n-back task. Other domain-specific effects have been observed in many lines of executive functions research, including those beyond the working memory domain. For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Other neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. Given this evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent interpretations of emotional stimuli with ambiguous valence.

<!-- Frequently, tasks in daily life require recruitment of working memory, but active working memory demands may affect concurrent processing. Many types of information can be held in working memory: strings of numbers, images, stimulus characteristics like brightness, spatial locations, and more. There is debate in the literature around the substrates of working memory and how this seemingly unitary construct is distributed across domain-specific subsystems (see [@baddeley_working_1986; @shah_separability_1996]). Recent work suggests though that working memory may contain more domain-specific subsystems than previously believed (e.g., affective working memory; e.g., @mikels_affective_2019). Similar to the work of Shah and colleagues -[@baddeley_working_1986], Mikels (find acutal study) showed ?double dissociation? of the affective working memory system from a more visually based working memory (i.e., maintenance of image brightness in memory). Similar domain-specific effects have been observed in many other lines of research, including those beyond the working memory domain. For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008], suggesting a division of subsystems. Given the behavioral and neurological evidence for dissociations of information domains in working memory, task interference and more, the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments (i.e., interpretations of emotional facial expressions). -->

<!-- While it is well known that distractors can undermine task performance [@hagen_effect_1967; cite, cite), some evidence suggests a role for domain-specificity in task interference.  For instance, domain-specific interference further exacerbates these task effects compared to domain-general stimuli [@gruber_effects_2001]. Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes. The relationship between these systems is bidirectional though, and often times working memory affects affective processing. One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008]. One explanation for mitigated emotional responding during concurrent working memory demands is load theory. This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands [@lavie_load_2004]. One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings. A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes. -->

## The present study
Given the evidence that positive interpretations of ambiguity rely on a regulatory mechanism, a demanding cognitive load could interfere with successful implementation of regulation strategies. Recently, Mattek and colleagues [-@mattek_differential_2016] showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to modal responses during interpretations of surprised expressions. However, there was no effect on subjective valence interpretations. Further, <!-- Just as phonological and visual cognitive loads and distractors showed domain-specificity [@burnham_components_2014], and--> domain-specificity effects in both behavioral and BOLD data [@kensinger_effect_2003; @whalen_emotional_2006 ;@egner_dissociable_2008] suggest that a domain-specific (i.e., emotional) cognitive load may differentially affect emotional judgments during interpretations of ambiguity. <!--In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing.--> Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials, as the high cognitive demand interferes with the regulatory mechanisms used to arrive at a positive interpretation. Further, we predict that higher working memory load trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations. 

<!-- domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues [-@mattek_differential_2016]  While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed. -->
<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive. -->
<!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite]. Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001]. This effect holds up in the emotional domain; for example, the Stroop task [@stroop_studies_1935] has been modified by some researchers to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008]. -->
<!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs. emotional) on ratings. Focus on EMO > NEU ratings and POS > NEG MDs. MT analyses could be supplementary material, but you'll be going down the rabbit hole.  -->
<!-- Recently, others have suggested a dynamic social trait space model for judgments of faces [@stolier_dynamic_2018], and it may be important to consider additional components of the categorization process, such as domain-specific loads.  -->
# Methods
## Participants
``` {r read data}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
```
Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln. The data from eight subjects were excluded due to technical difficulties resulting from an error in one of the experiment scripts. This left 50 individuals in the final sample for analysis. The mean age of the remaining sample was `r printnum(mean(data$age))` (`r printnum(sd(data$age))`), a majority of participants were female (`r printnum((sum(data$sex == "Female") / nrow(data))*100)`%), and all were white/caucasian without hispanic/Latinx ethnicity. All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the University of Nebraska-Lincoln Institutional Review Board (Approval #20141014670EP). Each participant received course credit for completing the study. 

## Material
### Stimuli
``` {r stimulus_t.test, include = FALSE}
stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/IAPS_Stim_List.xlsx")
shapiro.test(subset(stim.data, Condition == "POS")$Aro_Mn)
shapiro.test(subset(stim.data, Condition == "NEG")$Aro_Mn)
stim.t.test <- wilcox_test(subset(stim.data, Condition == "POS")$Aro_Mn, subset(stim.data, Condition == "NEG")$Aro_Mn)
```
The stimuli included faces from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets, as in previous work [@neta_primacy_2010; @brown_cortisol_2017]. The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scene stimuli were selected from the International Affective Picture System [@lang_international_2008]. A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = `r printnum(stim.t.test$z_val)`, p = `r printnum(stim.t.test$p.value)`). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1). 

## Procedure
After arriving at the lab, participants provided informed consent prior to completing the task. Participants were randomly assigned to complete one of the task versions, which included 144 [^1] trials split between working memory probe and face rating trials. The task was completed using MouseTracker software [@freeman_mousetracker:_2010] and participants responded with a mouse to indicate the appropriate response for the face ratings (i.e., "POSITIVE" or "NEGATIVE") and the memory probe (i.e., "YES" or "NO"). The trials were self-initiated; that is, the participant clicked a "start" button at the bottom of the screen at the beginning of each trial at their own pace. After initiating the trial, a fixation cross appeared (1000 ms), then participants viewed an image matrix, which the participants were instructed to remember for the duration of the trial. The image matrix was presented for 4000 ms and the image was either a low or high load matrix consisting of either emotional (equal positive and negative) or neutral images. After the image matrix a happy, angry, or surprised face appeared for 1000 ms and the participants rated the face by clicking on either the positive or negative response option. After the face rating, a single image probe appeared (5000 ms), and participants indicated whether or not the image probe was present in the previous image matrix. 

[^1]: Some versions of the task only included 142 trials due to a programming error. 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. Data preprocessing was completed in R using the mousetrap package [@kieslich_mouse-tracking_inpress]. First, percent negative ratings were calculated for happy, angry, and surprised faces across all trial types, as well as a percent correct score for the memory probe trials. After, trials were screened for RT outliers. Any trials that were greater than three standard deviations from the mean were removed from the analyses. Additionally, we removed the preceding face rating trial for any incorrect memory probe trials, as these trials can be considered a manipulation failure. 

Prior to completing the analyses, all data were assessed for normality using Shapiro-Wilks tests. We tested for differences in valence bias among the different working memory load conditions. Friedman's test was used to assess overall differences and pairwise comparisons were completed using Wilcoxon signed rank tests using Bonferroni correction. Next, we tested for differences among maximum deviations in each working memory load condition using a load (low, high) X domain (emotional, neutral) repeated-measures ANOVA.

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}

### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### assess normality ###
shapiro.test(data$lo.neu.sur_rate) # non-normal
shapiro.test(data$hi.neu.sur_rate) # non-normal
shapiro.test(data$lo.emo.sur_rate) # non-normal
shapiro.test(data$hi.emo.sur_rate) # non-normal

### make data long ###
friedman.data <- gather(data, key = "Condition", value = "Percent Negative Ratings",
       lo.neu.sur_rate, hi.neu.sur_rate, lo.emo.sur_rate, hi.emo.sur_rate)

### run Friedman's test and store results ###
friedman.results <- friedman.test(`Percent Negative Ratings` ~ Condition|subjID, data = friedman.data)

### Follow up wilcoxon tests ###
lo.emo.v.lo.neu <- wilcox_test(data$lo.emo.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.neu <- wilcox_test(data$lo.emo.sur_rate, data$hi.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.emo <- wilcox_test(data$lo.emo.sur_rate, data$hi.emo.sur_rate, paired = TRUE, conf.int = TRUE)
hi.emo.v.lo.neu <- wilcox_test(data$hi.emo.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)
hi.emo.v.hi.neu <- wilcox_test(data$hi.emo.sur_rate, data$hi.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.neu.v.hi.neu <- wilcox_test(data$hi.neu.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)

### same results with ANOVA ###

# aov.data <- friedman.data
# aov.data$load <- recode(aov.data$Condition, "lo.neu.sur_rate" = "low",
#                         "hi.neu.sur_rate"= "high",
#                         "lo.emo.sur_rate"= "low",
#                         "hi.emo.sur_rate"= "high")
# aov.data$type <- recode(aov.data$Condition, "lo.neu.sur_rate" = "neu",
#                         "hi.neu.sur_rate"= "neu",
#                         "lo.emo.sur_rate"= "emo",
#                         "hi.emo.sur_rate"= "emo")
# summary(aov(`Percent Negative Ratings` ~ load * type, data = aov.data))
```
Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different rank-order distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content, and this was true for both low and high loads. Low emotional load ratings were significantly more negative than low, Z = `r (printnum(lo.emo.v.lo.neu$z_val))`, p = `r (printp(lo.emo.v.lo.neu$p.value))`, neutral and high, Z = `r (printnum(lo.emo.v.hi.neu$z_val))`, p `r (printp(lo.emo.v.hi.neu$p.value))`, neutral loads. The same was true for high emotional load ratings and low, Z = `r (printnum(hi.emo.v.lo.neu$z_val))`, p `r (printp(hi.emo.v.lo.neu$p.value))`, and high, Z = `r (printnum(hi.emo.v.hi.neu$z_val))`, p `r (printp(hi.emo.v.hi.neu$p.value))`, neutral loads. However, there was no effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = `r (printnum(lo.emo.v.hi.emo$z_val))`, p = `r (printp(lo.emo.v.hi.emo$p.value))`, and neutral, Z = `r (printnum(lo.neu.v.hi.neu$z_val))`, p = `r (printp(lo.neu.v.hi.neu$p.value))`, load ratings were not significantly different [^2]. 
<!-- double check that this is true for the repeated measures ANOVA analysis too -->
``` {r plot figure 1, include = TRUE}
friedman.data$Condition <- factor(friedman.data$Condition, levels = c("lo.emo.sur_rate", "hi.emo.sur_rate",
                                                                      "lo.neu.sur_rate", "hi.neu.sur_rate"))
friedman.data$Condition <- recode(friedman.data$Condition, "lo.emo.sur_rate" = "Low Emotional", "hi.emo.sur_rate" = "High Emotional",
                                                            "lo.neu.sur_rate" = "Low Neutral", "hi.neu.sur_rate" = "High Neutral")
friedman.data$`Percent Negative Ratings` <- friedman.data$`Percent Negative Ratings` * 100
ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = Condition)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
  expand_limits(y=c(0, 100)) +
  theme_apa() +
  theme(axis.text.x=element_blank()) 
  
```

[^2]: These results are qualitatively the same when analyzing these data with a repeated measures ANOVA. 

``` {r MAD, include = FALSE}
###  MAD analyses ###
### check for normality ###
shapiro.test(data$lo.emo.sur_MAD) # not normal (p = .024)
shapiro.test(data$hi.emo.sur_MAD) # barely normal (p = .09)
shapiro.test(data$lo.neu.sur_MAD) # normal
shapiro.test(data$hi.neu.sur_MAD) # normal

MAD.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
MAD.long$load <- ifelse(MAD.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(MAD.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
MAD.long$type <- ifelse(MAD.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(MAD.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

MAD.anova <- aov(MAD ~ load * type, data = MAD.long)
summary.aov(MAD.anova)
MAD.anova <- tidy(MAD.anova)
```
Next, we assessed differences in maximum absolute deviation (MD) across the working memory trial conditions. While one of the conditions, low emotional MD, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions. There was a significant effect of load, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load")])`,`r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load")])`, such that MDs under high load were larger than trials with low load. There was no significant effect of domain on MDs, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "type")])`, nor an interaction of load by domain, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load:type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load:type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load:type")])`. 
``` {r MAD plot, include = TRUE}
MAD.long$Condition <- factor(MAD.long$Condition, levels = c("lo.emo.sur_MAD", "hi.emo.sur_MAD",
                                                                      "lo.neu.sur_MAD", "hi.neu.sur_MAD"))
MAD.long$Condition <- recode(MAD.long$Condition, "lo.emo.sur_MAD" = "Low Emotional", "hi.emo.sur_MAD" = "High Emotional",
                                                            "lo.neu.sur_MAD" = "Low Neutral", "hi.neu.sur_MAD" = "High Neutral")
ggplot(MAD.long, aes(Condition, MAD, fill = Condition)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
  theme_apa() +
  theme(axis.text.x=element_blank()) 

```
``` {r MAD map, include = FALSE}
suppressPackageStartupMessages(library(mousetrap)) 
# source MADFigure.R ??? 

```

# Discussion
The effect of high vs. low load is still not apparent in these data, just like Mattek et al. 2016. An alternative explanation is that the high load manipulation is not sufficiently difficult to recruit the targeted cognitive resources; however, future work will be needed to better test this alternative. 

Increased working memory demands (i.e., a higher cognitive load) do not always result in poorer performance on concurrent tasks. For instance Baddeley -[@baddeley_working_1986] reported that increasing load by adding digits to a rehearsed number did not affect accuracy on a concurrent verbal reasoning task--instead, there was an increase in the latency of response, a potential interference effect that did not alter overall accuracy. 

Previous work has shown that more positive interpretations of surprised faces are related to slower RTs. Our working hypothesis suggests that this delayed reaction is a result of deliberation and slower, top-down cognitive processing. It is interesting to note that, at least in these data, there is no such difference observed between the neutral and emotional WM trials, *even though* the emotional WM trials are overall more negative. Future work should tease apart why this may be. For instance, ... 

Future work should consider whether the representations of these emotional images in AWM (Reuter-Lorenz), or 

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
